Molecular Gas Kinematics and Spectral Energy Distribution Properties of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231

### 2016-12-12 WRITEUP/ms.tex
with DR's comment and changed focus of conclusion to feedback

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile with a conspicuous source-plane velocity
gradient suggests that
the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
In addition, we find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\eq(1.4\pmm0.3)\E{10}\,\Msun
and (2.0\pmm0.1)\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
The gas mass fraction of $f_{\rm gas}$\eq18\pmm4\% inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
We find lensing-corrected stellar and dust masses, an IR luminosity, and a
star formation rate of
$M_{*}$\eq(3\pmm1)\E{10}\,\Msun, $M_{\rm dust}$\ssim3\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU for RXS\,J1131$-$1231.
The source-plane morphologies of its gas and stellar populations
indicate that the star-formation activity may be as extended as the molecular gas reservoir.
We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{0.11}{0.08}\% which is higher
than the 
local value, suggesting that the bulk of the black hole mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.
\end{abstract}

@@

\subsection{PdBI \bco}
Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz) 
towards RXJ1131
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
Riechers).
Based on the CARMA \cco line redshift of $z_{\rm CO(3-2)}$\eq0.655,
the \bco line is redshifted to $\nu_{\rm obs}$\eq139.256\,GHz.
Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively.
This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
($\sim$\,$4.2$\,\kms).
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding calibration accuracy better than 15\%.

@@

The deconvolved source size FWHM obtained from fitting a single two-dimensional Gaussian 
to the integrated line emission in the image plane yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7,  
% In the image plane, the *convolved* size is 6.6"+/-0.5" x 4.5"+/-0.3". 
which is consistent with that obtained by visibility-plane fitting within the uncertainties. 
% UV plane: E_GAUSS: 4.5 +/- 0.1 x 3.5 +/- 0.2
Since the spatial distribution of the observed CO emission is unlikely to be fully described by a simple Gaussian
and appears to be a superposition of two components (top left panel of \Fig{CO21mom}), 
we also fit two Gaussians to the intensity map. 
This yields deconvolved source sizes of 
3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3, respectively.
The deconvolved source sizes of both models suggest that the gravitationally lensed CO emission is more extended 
than the optical 
``Einstein ring'', which has a diameter of $\sim$3\farcs6
(i.e., the ``Einstein ring'' formed by CO emission is likely to have a larger diameter compared to the optical one). 
This is consistent with the centroid position of the redshifted emission, which is along the quasar arc seen in the optical image, 
and the blueshifted emission, which is offset further to the SE (top right of \Fig{CO21mom}).
Therefore, the CO-emitting region in RXJ1131 is likely to be more extended than its stellar and quasar emission.

@@

\subsection{\cco Emission}
We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim$\,5$\sigma$ significance.
The \cco spectrum appears to be consistent with a double-peaked profile, as shown in \Fig{co32spec}, where
we over-plot spectra of the \bco and \cco lines.
We extract the peak fluxes and their corresponding uncertainties for the blue and red wing independently.
%For the blue wing, we find a peak line flux of 5.13\pmm1.43 Jy\,\kms beam\pmOne in the intensity map, indicating a $\gtrsim$3$\sigma$ detection for this component. 
%For the red wing, we find a peak flux of 11.45\pmm1.99\,Jy\,\kms beam\pmOne in the intensity map, 
% indicating a $\sim$\,6$\sigma$ detection. 
We find a peak line flux of 5.13\pmm1.43 Jy\,\kms beam\pmOne for the blue wing, indicating a $\gtrsim$3$\sigma$ detection for this component alone, and a peak line flux of 11.45\pmm1.99\,Jy\,\kms beam\pmOne for the red wing, 
indicating a $\sim$\,6$\sigma$ detection. 
We estimate a line intensity of 35.7\,$\pm$\,6.9\,Jy\,\kms (\Tab{obsprop}) by summing up fluxes over the FWZI
linewidth used to infer the \bco line intensity.

@@

We detect 2.2\,mm continuum emission at an
 integrated flux density of
1.2\pmm0.2 mJy, with a peak flux of
$S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne
centered on the lensing galaxy (\Fig{cont}).
% We note that the reported flux uncertainties do not include those from absolute flux calibration.
Slightly extended emission
along the lensed arc is also detected.
This suggests that we detect emission in both
the foreground and the background galaxy and that the
emission is marginally resolved along its major axis.
We subtract a point source model in the visibility-plane to remove the unresolved part of the
emission, which we here assume to be dominated by the foreground galaxy. The emission
in the residual map coincides spatially with the lensed arc. We measure a flux density 
of $S_{\nu}$\eq0.39\,$\pm$\,0.08\,mJy for this residual component.
This flux density is consistent with
the difference between the integrated and the peak flux density measured in the
original continuum map ($\sim$0.4 mJy). 
We therefore adopt $S_{\nu}$\eq0.39\pmm0.12 mJy as the best estimate for the 2\,mm continuum flux of 
the background galaxy (RXJ1131). 
We here quote a conservative error bar, which is derived by adding the uncertainty 
associated with the flux density of the 
point-source model ($\delta S_{\nu}$\eq0.088\,mJy) with
that of the peak flux in the residual map (0.08\,mJy) 
in quadrature. We caution that this does not account for the systematic uncertainties of the 
de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
We report the peak flux in the original map
($S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne) for the foreground galaxy, which
is the best estimate possible at the resolution of our observations, but we acknowledge that a non-negligible contribution from the background source to the peak flux cannot be ruled out.

@@

The VLA C-band continuum image in \Fig{cont} shows resolved emission from the
jets and the core of the foreground elliptical galaxy
as well as emission toward the background quasar.
Multiple peaks are seen along the arc with their centroids
coincident with the optical emission from the quasar.
We extract the flux densities for the lensing arc and the radio core in \Tab{photometry}.
We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.02\pmm0.07
for the foreground galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.35\pmm0.21 % differential
for the background galaxy by fitting
power-laws ($S_\nu \propto \nu^{\alpha}$) to their continuum fluxes at
5\,GHz and 2\,mm. 
The spectral slope derived for the background source is flatter than the typical slope of pure synchrotron emission \citep[$\alpha$\ssim$-$0.7; e.g.,][]{Andreani93a}. This likely suggests % {\bf DR: 3C273 flat-spectrum radio source BLAH}
that a fraction of the observed 2\,mm emission arises from thermal dust  emission. 
This spectral slope would be even shallower 
if the background source contributes to the unresolved fraction of the
2\,mm flux. This would also 
explain the flat spectrum found for the foreground galaxy, which is atypical of elliptical galaxies. 
Assuming a synchrotron slope of $\alpha$\ssim$-$0.7, we would expect
a flux density of $S_{\rm 2mm}$\eq0.122\pmm0.004 mJy at 2\,mm      % (139.256/4.8815)**-0.7 *1.273 = 0.122; error: 1.273 +/- 0.042 --> 0.042/1.273 * 0.122 = 0.004
for the background source due to synchrotron radiation,
and thus an excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy relative to this expectation
likely arises due to thermal dust emission.

% We thus adopt the flux excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy as
% thermal dust emission. % (0.12/0.39)^2 + (0.004/0.122)^2]^1/2 *  0.27

@@

\begin{figure}[!htbp]
\includegraphics[width=0.45\textwidth]{../Figures/de-lensedSpecCO21_complicated_unbinned_ylog.eps}
\caption{Top: the full resolution \bco spectrum (yellow histogram) and
the binned spectrum (dashed line) with the seven $\Delta v$\,$\sim$\,105\,\kms channels used for lens modeling. The
light blue histogram shows the ``intrinsic'' line profile of RXJ1131
after subtracting a contribution from its companion galaxy and
correcting for lensing using the magnification factor $\mu_{\rm L}$ as annotated by the horizontal bar shown
above each respective model channel.
Bottom: the ``intrinsic'' line profile of RXJ1131 (light blue) and of its companion (dark blue).
The y-axis is shown on log scale (top) and linear scale (bottom).
\label{fig:delensed}}
\end{figure}

@@

\subsubsection{Spatial Extent and Differential Lensing} \label{sec:differential}
In the image-plane integrated line map shown in \Fig{CO21mom}, the redshifted component is
cospatial with the Einstein ring that is seen in the
optical image, with most of its apparent flux originating along the lensed arc, 
whereas centroid of the blueshifted emission is offset to the SE of
the lensed arc. This suggests that the CO-emitting region in RXJ1131 is extended.
To further illustrate this, we show the
channel maps of 21.5\,\kms width and a spatial spectra map of 1\farcs5 resolution in
\Fig{chanmap} and \Fig{spatialSpec}, respectively. These figures
show that redshifted emission
is present to the west, peaking toward the lensing arc (black crosses in
\Fig{chanmap}), and shifts to the east with decreasing velocity
(blue wing).
This is consistent with the source plane positions in our models and
is suggestive of an extended CO emitting region.
%% spatial offset between AGN and the host
%In the channel maps in \Fig{CO21mom} and
%\Fig{chanmap}, the line center of the CO gas is not co-spatial with the optical quasar --- the point-like images along the lensing arc are
%offset to the NW of the CO line center emission.

@@

Previous studies of RXJ1131 find evidence for differential lensing across 
the {\it HST} $V$-, $I$-, and $H$-bands, where the
magnification factor varies from 10.9 to 7.8 \citepalias{Claeskens06a}.
This indicates that emission from different stellar populations 
within the host galaxy are dissimilar with respect to the caustic. 
%This imply that different stellar populations in the host galaxy are not co-spatial, and have  
%different spatial extents, or
%may be a result of dust extinction and reddening.
The best-fit lens models obtained here for different CO channel slices show that differential lensing also plays 
an important role in the observed \bco emission, with a magnification factor $(\mu_{\rm L})$ that varies
from 8.7 to 3.1 across different kinematic components (\Tab{model}).
The asymmetry in the line profile (\Fig{co21spec} and \Fig{delensed}) is therefore predominantly a result of
the redshifted CO-emitting gas being more strongly-magnified 
than the 
blueshifted component.
A secondary effect is likely a result of including emission from the companion in the most redshifted velocity channels.
The variation in $\mu_{\rm L}$ found across channels is consistent with the source plane
positions relative to the caustics in \Fig{model}, where the red wing
emission mainly originates near the cusp
of the caustic and the blue wing emission is located beyond the caustics.
In fact, the intrinsic line flux of the redshifted and
blueshifted emission in RXJ1131 (after subtracting a contribution from the companion)
are $I_{\small \bco}$\,=\,1.26\pmm 0.23 Jy\,\kms and 1.25\pmm0.23 Jy\,\kms, respectively,
implying an intrinsically symmetric line profile (\Fig{delensed}). This is consistent with the symmetric source-plane
velocity gradient in our lens model (\Fig{model} and \Fig{PV}).
% The difference in magnification factors between CO and optical-to-NIR
% may further indicate that the CO emitting region is more extended and/or
% has a spatial offset from the optical-to-NIR emission
% (\ie different positions and alignment relative to the caustics) given
% the lower magnification factor found for CO (median $\mu_{\rm L}$ = 5.5)
% than in NIR, while their spatial extents appear to be similar. But then it could just be because of the low resolution and
% the degeneracy between the intrinsic source size and the magnification factor.

@@

\subsection{\bco Dynamical Modeling} \label{sec:dynamics}
As discussed in \Sec{caveat}, we interpret RXJ1131 as a disk galaxy as it displays
a kinematically-ordered velocity gradient in the source-plane velocity map of CO emission,
a symmetric double-horned line profile (\Fig{delensed}, \Fig{model} and, left panel of \Fig{PV}), 
and a disk-like morphology in the source-plane reconstruction of optical-NIR emission
\citepalias{Claeskens06a}.
We extract a one dimensional position-velocity (PV) profile 
by assuming that the source-plane centroids of different velocity components
obtained from dynamical lens modeling
are dominated by the tangential component of the
true velocity vector of a rotating disk, i.e., each velocity component would 
be seen as lying along the major axis of a rotating disk if observed with sufficiently high angular resolution 
(see right panel of \Fig{PV}).
In this process, the positions for each velocity component (plotted as data points in the right panel of \Fig{PV})
are extracted along the best-fitted major axis, which is along a PA of 121\degr.

@@

\input{table_mbb}
In the first model, we attempt to constrain the power-law index by including
the 24\,$\micron$ data. Based on the resulting posterior PDFs, we find an apparent
IR luminosity (rest-frame 8\,$-$\,1000\,$\micron$) of 8.22\petm{2.75}{2.98}\E{12} \Lsun, a
\fir luminosity (rest-frame 42.5\,$-$\,122.5\,$\micron$) of
3.81\petm{1.92}{1.97}\E{12}\,\Lsun, and a
dust mass of 16\petm{5}{12}\E{8}\,\Msun, all of which are not corrected for lensing magnification.
For the mass absorption coefficient, we adopt
$\kappa$\,=\,2.64\,m$^2$kg\pmOne at rest-frame 125.0\,$\micron$
\citep{Dunne03a}.
The dust mass uncertainty does not
include that of the absorption coefficient.

@@

%
% %Tacconi13a: the best-fit MS, SFR would be 12.1 Msun/yr for MS given Mstar = 3e10.
% %sSFR (Gyr^-1) = 0.68 (Mstar/6.6e10)^-0.35((1+z)/2.2)^2.8 = 0.40 if RXJ on MS
The specific star formation rate (sSFR\eq SFR/$M_*$) of 4\petm{2.6}{2.4}\,Gyr\pmOne derived for RXJ1131
is $\lesssim$1.5$\sigma$ above the main sequence according to
the redshift-dependent ``main sequence'' relation in \citet[and references therein]{Tacconi13a}.
%  and is consistent with those of the \cite{dacunha10a} sample of local ULIRGs.
Given that RXJ1131 share similar \SF rate, \SF efficiency, and CO disk size as other ``main sequence'' disk galaxies,
the small elevation in sSFR over the main sequence at $z$\ssim0.7 suggests
that the \SF activity in RXJ1131 may be enhanced by interactions with the companion.

@@

Alternative scenarios 
e.g., outflow/inflow of gas in the BLR, viewing angle towards the accretion disk, and 
obscuration in the clumpy accretion disk
are more commonly invoked to explain velocity offsets between BLR and systemic redshift. 
Since the BLR lines of RXJ1131 show positive velocity offsets with respect to its systemic redshift, it may imply that 
obscuration may be causing the observed 
BLR line emission to be dominated by the gas that is flowing into the central BH, or the receding component of
the accretion disk.
\citet{Sluse07a} report a covering factor of 20\% for the accretion disk in RXJ1131
based on its broad \mgii absorption line at $z$\eq0.654.
Additionally, the centroids of the BLR lines in RXJ1131 may be biased towards longer wavelengths due to
microlensing \citep[\eg][]{Sluse07a, Sluse12a}, which may have
magnified the redshifted component of the compact BLR more strongly than its blueshifted component.
% gas motion (Woo+15, 16).

>>>>

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile with a conspicuous source-plane velocity
gradient suggests that
the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
In addition, we find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\eq(1.4\pmm0.3)\E{10}\,\Msun
and (2.0\pmm0.1)\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
The gas mass fraction of $f_{\rm gas}$\eq18\pmm4\% inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
We find a lensing-corrected stellar mass of
$M_{*}$\eq(3\pmm1)\E{10}\,\Msun, a star formation rate of SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU, and
a star formation efficiency and specific SFR comparable to non-quasar host galaxies at $z$\ssim1.
This together with a gas mass fraction consistent with the trend of evolution indicate 
that no quenching of star formation is seen in RXJ1131.
Our results therefore suggest that 
the decrease in molecular gas mass fraction towards lower redshift 
plays a dominant role 
in the decline of cosmic star formation history even in quasar host galaxies.
\end{abstract}

@@

\subsection{PdBI \bco}
Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz)
towards RXJ1131
were carried out using the IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
Riechers).
Based on the CARMA \cco line redshift of $z_{\rm CO(3-2)}$\eq0.655,
the \bco line is redshifted to $\nu_{\rm obs}$\eq139.256\,GHz.
Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively.
This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
($\sim$\,$4.2$\,\kms).
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding calibration accuracy better than 15\%.

@@

The deconvolved source size FWHM obtained from fitting a single two-dimensional Gaussian
to the integrated line emission in the image plane yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7,
% In the image plane, the *convolved* size is 6.6"+/-0.5" x 4.5"+/-0.3".
which is consistent with that obtained by visibility-plane fitting within the uncertainties.
% UV plane: E_GAUSS: 4.5 +/- 0.1 x 3.5 +/- 0.2
Since the spatial distribution of the observed CO emission is unlikely to be fully described by a simple Gaussian
and appears to be a superposition of at least two components (top left panel of \Fig{CO21mom}),
we also fit two Gaussians to the intensity map.
This yields deconvolved source sizes of
3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3, separated by $\sim$2\farcs2 in RA and $\sim$1\farcs7 in Dec.  % RA: 3-0.76; Dec: 2.49-.78
The deconvolved source sizes of both models suggest that the gravitationally lensed CO emission is more extended
than the optical
``Einstein ring'', which has a diameter of $\sim$3\farcs6
(i.e., the ``Einstein ring'' formed by CO emission is likely to have a larger diameter compared to the optical one).
This is consistent with the centroid position of the redshifted emission, which is along the quasar arc seen in the optical image,
and the blueshifted emission, which is offset further to the SE (top right of \Fig{CO21mom}).
Therefore, the CO-emitting region in RXJ1131 is likely to be more extended than its stellar and quasar emission.

@@

\subsection{\cco Emission}
We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim$\,5$\sigma$ significance.
The \cco spectrum appears to be consistent with a double-peaked profile, as shown in \Fig{co32spec}, where
we over-plot spectra of the \bco and \cco lines.
We extract the peak fluxes and their corresponding uncertainties for the blue and red wing independently.
%For the blue wing, we find a peak line flux of 5.13\pmm1.43 Jy\,\kms beam\pmOne in the intensity map, indicating a $\gtrsim$3$\sigma$ detection for this component.
%For the red wing, we find a peak flux of 11.45\pmm1.99\,Jy\,\kms beam\pmOne in the intensity map,
% indicating a $\sim$\,6$\sigma$ detection.
We find a peak line flux of 5.13\pmm1.43 Jy\,\kms beam\pmOne for the blue wing, indicating a $\gtrsim$3$\sigma$ detection for this component alone, and a peak line flux of 11.45\pmm1.99\,Jy\,\kms beam\pmOne for the red wing,
indicating a $\sim$\,6$\sigma$ detection.
We measure a line intensity of 35.7\,$\pm$\,6.9\,Jy\,\kms (\Tab{obsprop}) by summing up fluxes over the FWZI
linewidth used to infer the \bco line intensity.

@@

We detect 2.2\,mm continuum emission at an
 integrated flux density of
1.2\pmm0.2 mJy, with a peak flux of
$S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne
centered on the lensing galaxy (\Fig{cont}).
% We note that the reported flux uncertainties do not include those from absolute flux calibration.
Slightly extended emission
along the lensing arc is also detected.
This suggests that we detect emission in both
the foreground and the background galaxy and that the
emission is marginally resolved along its major axis.
We subtract a point source model in the visibility-plane to remove the unresolved part of the
emission, which we here assume to be dominated by the foreground galaxy. The emission
in the residual map coincides spatially with the lensing arc. We measure a flux density
of $S_{\nu}$\eq0.39\,$\pm$\,0.08\,mJy for this residual component.
This flux density is consistent with
the difference between the integrated and the peak flux density measured in the
original continuum map ($\sim$0.4 mJy).
We therefore adopt $S_{\nu}$\eq0.39\pmm0.12 mJy as the best estimate for the 2\,mm continuum flux of
the background galaxy (RXJ1131).
We here quote a conservative error bar, which is derived by adding the uncertainty
associated with the flux density of the
point-source model ($\delta S_{\nu}$\eq0.088\,mJy) with
that of the peak flux in the residual map (0.08\,mJy)
in quadrature. We caution that this does not account for the systematic uncertainties of the
de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
We report the peak flux in the original map
($S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne) for the foreground galaxy, which
is the best estimate possible at the resolution of our observations, but we acknowledge that a non-negligible contribution from the background source to the peak flux cannot be ruled out.

@@

The VLA C-band continuum image in \Fig{cont} shows resolved emission from the
jets and the core of the foreground elliptical galaxy
as well as emission toward the background quasar.
Multiple peaks are seen along the arc with their centroids
coincident with the optical emission from the quasar.
We extract the flux densities for the lensing arc and the radio core in \Tab{photometry}.
We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.02\pmm0.07
for the foreground galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.35\pmm0.21 % differential
for the background galaxy by fitting
power-laws ($S_\nu \propto \nu^{\alpha}$) to their continuum fluxes at
5\,GHz and 2\,mm.
The spectral slope derived for the background source is flatter than the typical slope of pure synchrotron emission \citep[$\alpha$\ssim$-$0.7; e.g.,][]{Andreani93a}. This likely suggests % {\bf DR: 3C273 flat-spectrum radio source BLAH}
that at least a fraction of the observed 2\,mm emission arises from thermal dust  emission.
This spectral slope would be even shallower
if the background source contributes to the unresolved fraction of the
2\,mm flux. 
In this case, the 2\,mm flux of the foreground galaxy would be lower than the value reported here and yield a steeper slope.
This would also
explain the flat spectrum found for the foreground galaxy, which is atypical of elliptical galaxies.
Assuming a spectral slope of $\alpha$\ssim$-$0.7 for synchrotron radiation in RXJ1131, we expect
a flux density of $S_{\rm 2mm}$\eq0.122\pmm0.004 mJy at 2\,mm.     % (139.256/4.8815)**-0.7 *1.273 = 0.122; error: 1.273 +/- 0.042 --> 0.042/1.273 * 0.122 = 0.004
The flux excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy therefore likely arises due to thermal dust emission.
% We thus adopt the flux excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy as
% thermal dust emission. % (0.12/0.39)^2 + (0.004/0.122)^2]^1/2 *  0.27

@@

\begin{figure}[!htbp]
\includegraphics[width=0.45\textwidth]{../Figures/de-lensedSpecCO21_complicated_unbinned_ylog.eps}
\caption{Top: the full resolution \bco spectrum (yellow histogram) and
the binned spectrum (dashed line) with the seven $\Delta v$\,$\sim$\,105\,\kms channels used for lens modeling. The
light blue histogram shows the ``intrinsic'' line profile of RXJ1131
after subtracting a contribution from its companion galaxy and
correcting for lensing using the magnification factor $\mu_{\rm L}$ as annotated by the horizontal bar shown
above each respective model channel.
Bottom: the ``intrinsic'' line profile of RXJ1131 (light blue) and of its companion (dark blue).
The y-axes are shown on a log scale.
\label{fig:delensed}}
\end{figure}

@@

\subsubsection{Spatial Extent and Differential Lensing} \label{sec:differential}
In the image-plane integrated line map shown in \Fig{CO21mom}, the redshifted component is
cospatial with the Einstein ring that is seen in the
optical image, with most of its apparent flux originating along the lensing arc,
whereas centroid of the blueshifted emission is offset to the SE of
the lensing arc. This suggests that the CO-emitting region in RXJ1131 is extended.
To further illustrate this, we show the
channel maps of 21.5\,\kms width and a spatial spectra map of 1\farcs5 resolution in
\Fig{chanmap} and \Fig{spatialSpec}, respectively. These figures
show that redshifted emission
is present to the west, peaking toward the lensing arc (black crosses in
\Fig{chanmap}), and shifts to the east with decreasing velocity
(blue wing).
This is consistent with the source plane positions in our models and
is suggestive of an extended CO emitting region.
%% spatial offset between AGN and the host
%In the channel maps in \Fig{CO21mom} and
%\Fig{chanmap}, the line center of the CO gas is not co-spatial with the optical quasar --- the point-like images along the lensing arc are
%offset to the NW of the CO line center emission.

@@

Previous studies of RXJ1131 find evidence for differential lensing across
the {\it HST} $V$-, $I$-, and $H$-bands, where the
magnification factor varies from 10.9 to 7.8 \citepalias{Claeskens06a}.
This indicates that emission from different stellar populations
within the host galaxy are dissimilar with respect to the caustic.
%This imply that different stellar populations in the host galaxy are not co-spatial, and have
%different spatial extents, or
%may be a result of dust extinction and reddening.
The best-fit lens models obtained here for different CO channel slices show that differential lensing also plays
an important role in the observed \bco emission, with a magnification factor $(\mu_{\rm L})$ that varies
from 8.7 to 3.1 across different kinematic components (\Tab{model}).
The asymmetry in the line profile (\Fig{co21spec} and \Fig{delensed}) is therefore predominantly a result of
the redshifted CO-emitting gas being more strongly-magnified
than the
blueshifted component.
A secondary reason is likely due to 
the inclusion of the emission of the companion in the most redshifted velocity channels.
The variation in $\mu_{\rm L}$ found across channels is consistent with the source plane
positions relative to the caustics in \Fig{model}, where the red wing
emission mainly originates near the cusp
of the caustic and the blue wing emission is located beyond the caustics.
In fact, the intrinsic line flux of the redshifted and
blueshifted emission in RXJ1131 (after subtracting a contribution from the companion)
are $I_{\small \bco}$\,=\,1.26\pmm 0.23 Jy\,\kms and 1.25\pmm0.23 Jy\,\kms, respectively,
implying an intrinsically symmetric line profile (\Fig{delensed}). This is consistent with the symmetric source-plane
velocity gradient in our lens model (\Fig{model} and \Fig{PV}).
% The difference in magnification factors between CO and optical-to-NIR
% may further indicate that the CO emitting region is more extended and/or
% has a spatial offset from the optical-to-NIR emission
% (\ie different positions and alignment relative to the caustics) given
% the lower magnification factor found for CO (median $\mu_{\rm L}$ = 5.5)
% than in NIR, while their spatial extents appear to be similar. But then it could just be because of the low resolution and
% the degeneracy between the intrinsic source size and the magnification factor.

@@

\subsection{\bco Dynamical Modeling} \label{sec:dynamics}
As discussed in \Sec{caveat}, we interpret RXJ1131 as a disk galaxy as it displays
a kinematically-ordered velocity gradient in the source-plane velocity map of the CO emission,
a symmetric double-horned line profile (\Fig{delensed}, \Fig{model} and, left panel of \Fig{PV}),
and a disk-like morphology in the source-plane reconstruction of the optical-NIR emission
\citepalias{Claeskens06a}.
We extract a one dimensional position-velocity (PV) profile
by assuming that the source-plane centroids of different velocity components
obtained from dynamical lens modeling
are dominated by the tangential component of the
true velocity vector of a rotating disk, i.e., each velocity component would
be seen as lying along the major axis of a rotating disk if observed with sufficiently high angular resolution
(see right panel of \Fig{PV}).
In this process, the positions for each velocity component (plotted as data points in the right panel of \Fig{PV})
are extracted along the best-fitted major axis, which is along a PA of 121\degr.

@@

\input{table_mbb}
In the first model, we attempt to constrain the power-law index by including
the 24\,$\micron$ data. Based on the resulting posterior PDFs, we find an apparent
IR luminosity (rest-frame 8\,$-$\,1000\,$\micron$) of 8.22\petm{2.75}{2.98}\E{12} \Lsun, a
\fir luminosity (rest-frame 42.5\,$-$\,122.5\,$\micron$) of
3.81\petm{1.92}{1.97}\E{12}\,\Lsun, and a
dust mass of 16\petm{5}{12}\E{8}\,\Msun, none of which are corrected for lensing magnification.
For the mass absorption coefficient, we adopt
$\kappa$\,=\,2.64\,m$^2$kg\pmOne at rest-frame 125.0\,$\micron$
\citep{Dunne03a}.
The dust mass uncertainty does not
include that of the absorption coefficient.

@@

%
% %Tacconi13a: the best-fit MS, SFR would be 12.1 Msun/yr for MS given Mstar = 3e10.
% %sSFR (Gyr^-1) = 0.68 (Mstar/6.6e10)^-0.35((1+z)/2.2)^2.8 = 0.40 if RXJ on MS
The specific star formation rate (sSFR\eq SFR/$M_*$) of 4\petm{2.6}{2.4}\,Gyr\pmOne derived for RXJ1131
is $\lesssim$1.5$\sigma$ above the main sequence according to
the redshift-dependent ``main sequence'' relation in \citet[and references therein]{Tacconi13a}.
%  and is consistent with those of the \cite{dacunha10a} sample of local ULIRGs.
Given that RXJ1131 share similar \SF rate, \SF efficiency, and CO disk size as other ``main sequence'' disk galaxies,
the small elevation in sSFR over the main sequence at $z$\ssim0.7 suggests
that the \SF activity in RXJ1131 may be enhanced by interactions with the companion.
In addition, a SFE and a sSFR similar to those of high-$z$ disk 
galaxies, which are not known to host an AGN,
together with a molecular gas mass fraction that follows the reported trend of evolution (\Sec{frac})
suggest that no quenching of star formation is observed in RXJ1131, despite 
that fact that it is hosting a quasar.
Hence, the decline in star formation history since $z$\ssim2 even for AGN host galaxies is likely
a manifestation of the evolution in the molecular gas content rather than negative feedback driven by their central AGNs.

@@

Alternative scenarios 
e.g., outflow/inflow of gas in the BLR, viewing angle towards the accretion disk, and 
obscuration in the clumpy accretion disk
are more commonly invoked to explain velocity offsets between BLR and systemic redshift. 
Since the BLR lines of RXJ1131 show positive velocity offsets with respect to its systemic redshift, it may imply that 
the observed 
BLR line emission is dominated by the gas that is flowing into the central BH, or by the receding component of
the accretion disk, owing to the viewing angle or the obscuration in the accretion disk.
\citet{Sluse07a} report a covering factor of 20\% for the accretion disk in RXJ1131
based on its broad \mgii absorption line at $z$\eq0.654.
Additionally, the centroids of the BLR lines in RXJ1131 may be biased towards longer wavelengths due to
microlensing \citep[\eg][]{Sluse07a, Sluse12a}, which may have
magnified the redshifted component of the compact BLR more strongly than its blueshifted component.
% gas motion (Woo+15, 16).
